Containers and R---the Rockerverse and beyond

### 2020-01-18 manuscript.Rmd
update title
one sentence per line

Such RApache applications have been used at [rapporter.net](http://rapporter.net), transforming parametrized R Markdown-like documents into interactive web applications for reporting. A similar design was implemented at CARD.com, where the optimization of the acquisition flow and the real-time analysis of debit card transactions both relied on an efficient combination of Rserve and RApache running in Docker containers: the R session behind Rserve acted as a read-only, exteremely fast and scalabale, in-memory database for the many concurrent RApache processes responding to the live-scoring requests of other components of the company. Similar dockerized R scripts were responsible for the ETL processes and even the client-facing email, text message and push notification alerts sent in real-time on the card transaction. The related Docker images were made available at [https://github.com/cardcorp/card-rocker](https://github.com/cardcorp/card-rocker), which are extending `rocker/r-base` eg with an SSH client and workaround for being able to mount SSH keys from the host, Pandoc, the AWS SDK and Java -- which latter was required at that time to be able to easily use the Amazon Web Services via their Java SDK, eg to run R consumers reading from a Kinesis stream, deployed as a dockerized ECS service. The main learnings from using R in Docker was the imporance of not only pinning the R package versions via MRAN, but also moving away from Debian testing to an LTS distribution to minimize the risk of breaking the automated builds of the Docker images and/or production jobs.

>>>>

Such RApache applications have been used at [rapporter.net](http://rapporter.net), transforming parametrized R Markdown-like documents into interactive web applications for reporting.
A similar design was implemented at CARD.com, where the optimization of the acquisition flow and the real-time analysis of debit card transactions both relied on an efficient combination of Rserve and RApache running in Docker containers:
the R session behind Rserve acted as a read-only, exteremely fast and scalabale, in-memory database for the many concurrent RApache processes responding to the live-scoring requests of other components of the company.
Similar dockerized R scripts were responsible for the ETL processes and even the client-facing email, text message and push notification alerts sent in real-time on the card transaction.
The related Docker images were made available at [https://github.com/cardcorp/card-rocker](https://github.com/cardcorp/card-rocker), which are extending `rocker/r-base`, e.g., with an SSH client and workaround for being able to mount SSH keys from the host, Pandoc, the AWS SDK and Java -- which latter was required at that time to be able to easily use the Amazon Web Services via their Java SDK, eg to run R consumers reading from a Kinesis stream, deployed as a dockerized ECS service.
The main learnings from using R in Docker was the imporance of not only pinning the R package versions via MRAN, but also moving away from Debian testing to an LTS distribution to minimize the risk of breaking the automated builds of the Docker images and/or production jobs.
